Exploring Nonlinear Atmospheric Influences on Temperature Using Polynomial Regression at Vancouver International Airport

### 2024-12-10 paper/paper.qmd
update paper format

Some scholars have examined the changing climate. @xu_melting_2009 analyzes the effects of rising temperatures in the Himalayas, highlighting increased frequency and duration of extreme events and shifts in ecosystems. These changes pose challenges to water supply, agriculture, and human populations. @visser_eliminating_2021 investigates the relationship between precipitation and temperature using data from the Australian Bureau of Meteorology. Visser's regression model indicates that average precipitation intensities increase with temperature, suggesting more intense rainfall in a warmer climate. The role of sea level pressure is also significant. @wills_systematic_2022 note that observed trends in sea level pressure have caused slight cooling in the eastern equatorial Pacific. However, as @zhang_economic_2017 argues, much of the research has focused on temperature and precipitation. @zhang_economic_2017 expands on this by incorporating additional predictors—relative humidity and wind speed—and concludes, using data from the Ministry of Agriculture of China, that these variables are important in understanding climate dynamics.

@@

According to the glossary published by @meteorological_service_of_canada_past_2023, Each day, measurement of temperature, rain, snow, precipitation, and gust speed are recorded. The wind and gust speed are measured in km/h with anemometer dials at a standard height of 10 meters above the ground. Rain and precipitation are measured in millimeter using the standard Canadian rain gauge, a cylindrical container 40 cm high and 11.3 cm in diameter. Snow is measured in centimeters at several points that appear representative of the immediate area and then averaged. These raw data are combined to one entry and added to the historical climate database with a generated climate id and the station's location and id. Each row also has the month and year of the data measured.

@@

results <- data.frame(
  Metric = c("SSR", "TSS", "R2", "R2-Train", "MSE-Train", "MSE-Test"),
  Value = c(SSR, TSS, R2, R2T, mse_train, mse_test)
)
results$Value <- round(results$Value, 2)

@@

### Limitations on the Model LP

>>>>

Some scholars have examined the changing climate. @xu_melting_2009 analyzes the effects of rising temperatures in the Himalayas, highlighting increased frequency and duration of extreme events and shifts in ecosystems. These changes pose challenges to water supply, agriculture, and human populations. @visser_eliminating_2021 investigates the relationship between precipitation and temperature using data from the Australian Bureau of Meteorology. Visser's regression model indicates that average precipitation intensities increase with temperature, suggesting more intense rainfall in a warmer climate. The role of sea level pressure is also significant. @wills_systematic_2022 note that observed trends in sea level pressure have caused slight cooling in the eastern equatorial Pacific. However, as @zhang_economic_2017 argues, much of the research has focused on temperature and precipitation. @zhang_economic_2017 expands on this by incorporating additional predictors (relative humidity and wind speed) and concludes, using data from the Ministry of Agriculture of China, that these variables are important in understanding climate dynamics.

@@

According to the glossary published by @meteorological_service_of_canada_past_2023, each day, measurement of temperature, rain, snow, precipitation, and gust speed are recorded. The wind and gust speed are measured in km/h with anemometer dials at a standard height of 10 meters above the ground. Rain and precipitation are measured in millimeter using the standard Canadian rain gauge, a cylindrical container 40 cm high and 11.3 cm in diameter. Snow is measured in centimeters at several points that appear representative of the immediate area and then averaged. These raw data are combined to one entry and added to the historical climate database with a generated climate id and the station's location and id. Each row also has the month and year of the data measured.

@@

results <- data.frame(
  Metric = c("SSR", "TSS", "R2-Test", "R2-Train", "MSE-Train", "MSE-Test"),
  Value = c(SSR, TSS, R2, R2T, mse_train, mse_test)
)
results$Value <- round(results$Value, 2)

@@

### Limitation on the Model LP
